\section{\textbf{Introduction}}\label{sec:Introduction}
Hybrid broadcast broadband TV (or HbbTV) is a global
initiative aimed at harmonizing the broadcast and broadband
delivery of entertainment services to consumers through
connected TVs, set-top boxes and multiscreen devices. The
HbbTV specification is developed by industry leaders to improve
the video user experience for consumers by enabling innovative,
interactive services over networks. The specification
uses elements of existing specifications from other standards
including OIPF, CEA, DVB, MPEG-DASH and W3C. With
the incorporation of activities from the Open IPTV Forum
(OIPF) in 2014 and Smart TV Alliance in 2016, HbbTV is able
to address service providers and technology suppliers for IPTV
services as well as the combined scope of broadcast and overthetop services \footnote{https://www.hbbtv.org/news-events/hbbtv-releases-version-2018-2-of-the-hbbtv-conformance-test-suite//}. Jede Antwort zhlt is the famous german
game show, theme of the show is to present questions and
for each correct answer participants get cash prizes. There are many other games show on same theme and mostly they catch
their audience attention with the valuable information they
provide in questions. And they make it more interesting by
awarding money on each answer\cite{hbbtv}. RBB-Quiz Plugins objective
is to make Jede Antwort zhlt more interesting for audience
watching game show at home. Quiz plugin will allow viewers
to interact with this TV, and they well be able to play quiz
along with the game show. This interactive experience will
catch more engagement of home audience, and show will
become more interesting for them as they will feel like they are
actually in the show and playing. MPAT takes up the concept
of web-page creation tools like WordPress, which allow users
to easily build a small to medium web site from pre-defined
templates and plug-ins, and adapts it to HbbTV  \footnote{https://github.com/MPAT-eu/MPAT-theme/blob/master/getContent.php}. So, well
be using plugin feature of wordpress to interact with wordpress
and MPAT powers. Firstly, this plugin will show the video of
quiz show on viewers Hbbtv screen, and when then host will
ask question on show, our plugin will also trigger an event
to show some components on screen. User wills interact with
these components by using his remote and he/she will submit
answer\cite{MPAT}. If the answer will be right, then user will get score
which will be update on the screen after the host will reveal
answer in the show. Secondly, before the broadcast of tv show
an editor will also interact with the admin panel of quiz plugin,
where he/she will be able to configure questions, answers,
time stamps and worth of question. Events on the viewer side
will be triggered on screen, by using all these details provided
by editor on admin panel by the editor.