\section{\textbf{FUTURE WORK}}\label{sec:FUTURE WORK} 
The RBB Quiz plugin was designed to meet basic requirements
of a given use case. Its functionality and design can be
improved to great extent.

\begin{itemize}
 
\item Designers Functionality
\item  Admin panel improvements
\item  Improvement of Score Algorithm
\item  Right Answer Detection with Colors
 
\end{itemize}

components. Which will be done by a new editor
called Designer. The designer will have its own designer panel
where he will be able to submit design files. So, in the new
version size, location, color, and other styling attributes wont
be static and the designer will be able to customize them easily.
There are a couple of things to improve in the admin panel.
Fist of all, being flexible to the number of answers. Right
now we have static with three possible number of answers as
in Jede Antwort zhlt but, It can be improved to the dynamic
number of answer possibility for other quiz shows of similar
genres.

Some HbbTV providers the ability to fast forward programs,
currently, in our application, we are assuming as the viewer
cant forward broadcasted Video. So, if the user will have the
power to forward streamed video then it might show wrong
score.


We can optimize the algorithm so that a user can submit
the answer once for each question and there wont be double
additions in score in any case.
In the current version, we are validating answers by using
information provided by the administrator. A more complex
and efficient approach can be introduced so that the application
can detect colors in real-time and validate answers for each
question. It will surely be a bit complex task to implement,
but by using color detection we can reduce the workload of
administrator.



 